\section*{Pushing--Medium Model: Passed Tests}

\subsection*{1. Classical \& Relativistic Benchmarks}
\begin{itemize}
    \item Light bending by a point mass --- matches GR deflection angle for solar--grazing rays within numerical tolerance.
    \item Shapiro time delay --- correct radar signal delay near massive bodies.
    \item Gravitational redshift --- matches GR frequency shift between static observers in a potential well.
    \item Perihelion precession --- correct anomalous advance for Mercury--like orbits.
    \item Gravitational lensing geometry --- image positions/magnifications for simple lenses match GR.
    \item Weak--field limit --- reduces to Newtonian gravity for slow speeds and shallow potentials.
\end{itemize}

\subsection*{2. Dynamical \& Wave--Related Tests}
\begin{itemize}
    \item Frame--drag analogue --- rotating flow fields reproduce Lense--Thirring--type precession.
    \item Gravitational wave propagation --- TT--like perturbations in $n(\mathbf{r},t)$ travel at $c$ and produce quadrupole strain patterns.
    \item Energy conservation --- no secular drift in total energy for bound orbits in static fields.
    \item Radiation reaction consistency --- inspiral rates match GR's quadrupole formula in the weak--field limit.
\end{itemize}

\subsection*{3. Cosmological \& Large--Scale Checks}
\begin{itemize}
    \item Hubble--law mimicry --- large--scale, time--dependent $n$ fields reproduce linear redshift--distance relation.
    \item Cluster/galaxy lensing --- extended $n$ profiles match observed shear without exotic matter.
    \item Structure growth rates --- perturbation growth matches $\Lambda$CDM when tuned to the same expansion history.
\end{itemize}

\subsection*{4. Emergent / Non--GR--Allowed Phenomena}
\begin{itemize}
    \item Gravitational valves --- one--way transmission regions for light/matter.
    \item Directional gating --- asymmetric $n$ + $\mathbf{u}_g$ patterns bias motion by direction.
    \item Dynamic traps --- time--varying wells capture/release on command.
    \item Beam steering \& splitting --- arbitrary deflection/splitting of beams.
    \item Frequency--dependent bending --- chromatic gravitational lensing via dispersive $n$.
\end{itemize}

\subsection*{5. Internal Consistency \& Robustness}
\begin{itemize}
    \item Parameter economy --- passed all core tests with minimal free parameters.
    \item Superposition stability --- static, dynamic, and flow components combine without instability.
    \item Reproducibility --- all results regenerable from documented code/parameters.
    \item Portability --- same results across platforms/compilers in proof--passing codebase.
\end{itemize}
